---
title: "Activity Graphs"
author: "Morgan Ferrans"
date: "10/28/2021"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)

```

```{r}
library(ggplot2)
library(dplyr)
load(file = "activitygraphsenv.RData")
```
---
#PLOTTING ACTIVITY
Setup
---
Store weeks old as a factor 
```{r}
weeklyintervaldf$weeksold<-as.factor(weeklyintervaldf$weeksold)
indiv_weekly_dev$weeksold<-as.factor(indiv_weekly_dev$weeksold)
```
List of desired hourly time breaks for graph x axis tick marks
```{r}
hours_list<-c("08:00","09:00","10:00","11:00","12:00","13:00","14:00","15:00","16:00","17:00","18:00","19:00","20:00","21:00","22:00")
```



# MEAN ACTIVITY COUNT GRAPHS (raw mean activity, not deviance)
---
#### INDIVIDUAL GRAPH OF RAW (MEAN) ACTIVITY COUNTS FOR 1 INDIVIDUAL PUPPY FOR 1 INDIVIDUAL WEEK
```{r}
#Arthur, 8 weeks
#can add ylim(-500,2500)
ggplot(subset(intervaldf,weeksold=="16" & name=="Stanley"), aes(x=intervaltime, y=interval_avg_activity, group=1)) + geom_line() + ggtitle("Stanley: 16 weeks") + xlab("Time") + ylab("Mean Activity Counts") + labs(colour = "Age (weeks)") +
  scale_x_discrete(breaks=hours_list)
```

#### GRAPH OF RAW (MEAN) ACTIVITY COUNTS GROUPED BY PUPPY) FOR 1 SPECIFIC WEEK
```{r}
ggplot(subset(intervaldf,weeksold=="8"), aes(x=intervaltime, y=interval_avg_activity, group='name')) + geom_line(aes(colour=name)) + ggtitle("Group Activity Counts: 8 weeks") + xlab("Time")+ ylab("Mean Activity Counts") + labs(colour = "Puppy") + scale_x_discrete(breaks=hours_list)

ggplot(subset(intervaldf,weeksold=="18"), aes(x=intervaltime, y=interval_avg_activity, group='name')) + geom_line(aes(colour=name)) + ggtitle("Group Activity Counts: 18 weeks") + xlab("Time")+ ylab("Mean Activity Counts") + labs(colour = "Puppy") + scale_x_discrete(breaks=hours_list)
```

#### COMPARE TWO PUPPIES' RAW MEAN ACTIVITY COUNTS FOR 1 SPECIFIC WEEK
```{r}
###graph is now fixed!
ggplot(subset(intervaldf,name=="Sassy"&weeksold==8|name=="Arthur"&weeksold==8), aes(x=intervaltime, y=interval_avg_activity, group=name)) + geom_line(aes(colour=name)) + ggtitle("Mean Activity Counts: 8 weeks") + xlab("Time")+ ylab("Mean Activity Counts") + labs(colour = "Puppy") + scale_x_discrete(breaks=hours_list)
```

#### GROUP AVG OF RAW (MEAN) ACTIVITY COUNTS FOR 1 INDIVIDUAL WEEK
```{r}
#8 weeks
ggplot(subset(weeklyintervaldf,weeksold=="8"), aes(x=intervaltime, y=interval_weekly_avg, group=1)) + geom_line() + ggtitle("Group: 8 weeks") + xlab("Time") + ylab("Mean Activity Counts") + labs(colour = "Age (weeks)") + scale_x_discrete(breaks=hours_list)

#20 weeks
ggplot(subset(weeklyintervaldf,weeksold=="20"), aes(x=intervaltime, y=interval_weekly_avg, group=1)) + geom_line() + ggtitle("Group: 20 weeks") + xlab("Time") + ylab("Mean Activity Counts") + labs(colour = "Age (weeks)") + scale_x_discrete(breaks=hours_list)
```

#### GRAPHS OF ALL WEEKS OVERLAID (USING ENTIRE GROUP RAW MEAN ACTIVITY COUNTS)
```{r}
ggplot(weeklyintervaldf, aes(x=intervaltime, y=interval_weekly_avg, group=weeksold)) + geom_line(aes(colour=weeksold)) + ggtitle("Group: 8-20 weeks") + xlab("Time")+ ylab("Mean Activity Counts") + labs(colour = "Age (weeks)") + scale_x_discrete(breaks=hours_list)
```

#### GRAPHS OF GROUP: 8 VS 20 WEEKS (RAW MEAN ACTIVITY COUNTS)
```{r}
ggplot((subset(weeklyintervaldf,weeksold=="8" | weeksold=="20")), aes(x=intervaltime, y=interval_weekly_avg, group=weeksold)) + geom_line(aes(colour=weeksold)) + ggtitle("Group: 8 vs. 20 weeks") + xlab("Time") + ylab("Mean Activity Counts") + labs(colour = "Age (weeks)") + scale_x_discrete(breaks=hours_list)

```

####  GRAPHS OF GROUP: 8, 14, & 20 WEEKS
```{r}
ggplot((subset(weeklyintervaldf,weeksold=="8" | weeksold=="14"| weeksold=="20")), aes(x=intervaltime, y=interval_weekly_avg, group=weeksold)) + geom_line(aes(colour=weeksold)) + ggtitle("Group: 8, 14, & 20 weeks") + xlab("Time") + ylab("Mean Activity Counts") + labs(colour = "Age (weeks)") + scale_x_discrete(breaks=hours_list)

```



