---
title: "Sleep Data"
author: "Morgan Ferrans"
date: "10/28/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)

```

```{r}
library(ggplot2)
library(tidyverse)
load(file = "activitygraphsenv.RData")
```


# DATA FRAMES
```{r}
head(sleepbouts)
head(sleepbouts2)
```


---
#PLOTTING REST/WAKE BOUTS
---

Compare average rest/wake bout durations in 1 individual week
```{r}
ggplot(subset(sleepbout_weeklyavg,weeksold=="20"), aes(x=state, y=Mean_mins))+ geom_col(aes(fill=state)) + ggtitle("Average Sleep/Awake Bout Duration: 20 weeks") + xlab("State")+ ylab("Mean State Duration (min)") + labs(colour = "State")
```
Compare average rest/awake bout durations for each week
```{r}
ggplot(subset(sleepbout_weeklyavg,state=="awake"), aes(x=weeksold, y=Mean_mins))+ geom_col(aes(fill=weeksold)) + ggtitle("Avg Duration of Awake Bouts by Week") + xlab("Weeks Old")+ ylab("Mean State Duration (min)") + labs(colour = "Age (weeks)")

ggplot(subset(sleepbout_weeklyavg,state=="rest"), aes(x=weeksold, y=Mean_mins))+ geom_col(aes(fill=weeksold)) + ggtitle("Avg Duration of Rest Bouts by Week") + xlab("Weeks Old")+ ylab("Mean State Duration (min)") + labs(colour = "Age (weeks)")

```
Total Minutes of Rest by Week
```{r}
ggplot(subset(sleepbout_weeklyavg,state=="rest"), aes(x=weeksold, y=Total_mins))+ geom_col(aes(fill=weeksold)) + ggtitle("Average Total Rest by Week") + xlab("Weeks Old")+ ylab("Total Rest (min)") + labs(colour = "Age (weeks)")
```
AVG REST HOME VS. DPK 
```{r}
weeks<-c(8:20)

ggplot(subset(sleepbout_weeklyavg_rearing,state=="rest"), aes(x=weeksold, y=Mean_mins, colour=rearing, group=rearing)) + geom_point() + geom_line() + ggtitle("Avg Duration of Rest Bouts by Week: Home vs. DPK") + xlab("Weeks Old")+ ylab("Avg State Duration (min)") + labs(colour = "Rearing") + scale_x_continuous(breaks=weeks)

ggplot(subset(sleepbout_weeklyavg_rearing,state=="rest"), aes(x=weeksold, y=Total_mins, colour=rearing, group=rearing)) + geom_point() + geom_line() + ggtitle("Average Total Rest by Week: Home vs. DPK") + xlab("Weeks Old")+ ylab("Rest (mins)") + labs(colour = "Rearing") + scale_x_continuous(breaks=weeks)
```



  #BY PUPPY
---
Bar graph: Mean State Duration for 1 puppy by weeks
```{r}
ggplot(subset(sleepbout_weeklyavg_bypuppy, name=="Leo"), aes(x=weeksold, y=Mean_mins))+ geom_col(aes(fill=state)) + ggtitle("Leo: Mean Rest State Duration by Week") + xlab("Weeks Old")+ ylab("Mean State Duration (min)") + labs(colour = "Age (weeks)")+ scale_x_continuous(breaks=weeks)
```
Line graph: Mean State Duration for 1 puppy by weeks
```{r}
ggplot(subset(sleepbout_weeklyavg_bypuppy, name=="Leo"), aes(x=weeksold, y=Mean_mins, group=state))+ geom_line(aes(colour=state)) + ggtitle("Leo: Mean Rest State Duration by Week") + xlab("Weeks Old")+ ylab("Mean State Duration (min)") + labs(colour = "Age (weeks)")+ scale_x_continuous(breaks=weeks)
```
Line graph: mean rest state duration by week for each puppy
```{r}
ggplot(subset(sleepbout_weeklyavg_bypuppy, state=="rest"), aes(x=weeksold, y=Mean_mins, group=name))+ geom_line(aes(colour=name)) + ggtitle("Mean Rest State Duration by Week") + xlab("Weeks Old")+ ylab("Mean State Duration (min)") + labs(colour = "Age (weeks)")+ scale_x_continuous(breaks=weeks)
```
